From Net-Zero to Net-Negative: Assessing \hydrogen{} and \carbon{} Network Strategies in Europe

### 2023-11-06 report/submissions/journal/paper/paper.tex
add sankey plot, further write methodology

@@

Carbon-neutral energy is provided by wind, solar, biomass and hydro. Solar and wind power can be expanded according to land-use constrained in alignment with

, modeling the transmission and expansion of electricity (on extra-high voltage level), gas, and optionally \hydrogen{} and \carbon{}.

@@

Biomass usage in each region is bound by its biomass potential, but inter-regional biomass transport is permitted with transport costs considered. We restrict the electric transmission system's expansion to 20\% of its current capacity, acknowledging the challenges in inaugurating new transmission projects. The geographical spread of emissions from various industries is derived from~\cite{piamanzGeoreferencedIndustrialSites2018}, totaling 158~Mt \carbon{} annually.

@@

Addressing climate targets, we define three \carbon{} target scenarios:
\begin{itemize}
    \item[] \textit{Net-zero:} Annual net-zero emissions, aligning with the EU's 2050 target.
    \item[] \textit{5\% Net-negative:} Annual net-negative emissions of 5\% of 1990 emissions or 230~Mt \carbon{}.
    \item[] \textit{10\% Net-negative:} 10\% of 1990 emissions net-negative annually, or 460~Mt \carbon{}.
\end{itemize}
Unless otherwise mentioned, our reference is the Net-zero scenario. For 5\% Net-negative and 10\% Net-negative scenarios, the carbon sequestration potential is adjusted to 400~Mt/a and 600~Mt/a, respectively.

@@

\begin{figure*}[ht!]
    \centering
    % \includegraphics*[width=\linewidth]{cost_area.pdf}
    \caption[short]{Total annual system cost for the sector-coupled system with different levels of carbon sequestration potential, with (left) and without (right) \carbon{} network. "Gas Infrastructure" combines gas facilities for power and heat production, "H$_2$ Infrastructure" combines H$_2$ production, transport and re-electrification. Regardless of the implementation of a \carbon{} network, the system cost decrease as sequestration increases. Due to an increased flexibility from fossil carriers with subsequent sequestration, the need for FT synthesis and \hydrogen{} electrolysis and the corresponding renewable power supply is reduced.
        % TODO: mention details on the grouped technologies
    }
    \label{fig:cost_area}
\end{figure*}

@@

Figure~\ref{fig:operation_area_carbon_co2network} confirms our previous results and shows that FT synthesis production decreases with sequestration availability. At the same time, integrated carbon capture from Gas Combined Heat and Power (CHP) plants, Allam Cycle plants, Steam Methane Reforming (SMR) and DAC increases. Other technologies are constant across varying levels of sequestration due to different reasons: biomass is bound by its maximum available potential (as reported in~\cite{europeancommissionjointresearchcentreENSPRESOBIOMASS2019}); the industry processes with their associated emissions are set to fixed values; the methanol production is bound by a lower limit representing the demand from the shipping sector.

>>>>

The European Union's aim to become climate-neutral by 2050 require

@@

Carbon-neutral energy is provided by wind, solar, biomass and hydro. Weather-dependent power potentials for solar, wind and hydro per region and time-stamp are calculated from reanalysis and satellite data sets Copernicus ERA5~\cite{hersbachERA5GlobalReanalysis2020} and Surface Radiation Data Set - Heliosat~\cite{pfeifrothSurfaceRadiationData2017}  using the open-source tool~\cite{hofmannAtliteLightweightPython2021}.
Solar and wind power can be expanded in alignment with eligible land-use restrictions calculated on the basis of~\cite{eeaCorineLandCover2012,eeaNatura2000Data2016}. The biomass potential is calculated from the European Commission's Joint Research Centre's ENSPRESO database~\cite{enspreso_database} and the JRC-EU-TIMES model~\cite{instituteforenergyandtransportjointresearchcentreJRCEUTIMESModelBioenergy2015}. Its usage in each region is bound by its biomass potential, but inter-regional biomass transport is permitted with transport costs considered.

Salt caverns for \hydrogen{} storage are derived from~\cite{caglayanTechnicalPotentialSalt2020}.

Industrial energy demand and excess heat potentials are calculated per node on the basis of~\cite{hotmaps_industrial_db}.

% use https://pypsa-eur.readthedocs.io/en/latest/licenses.html

@@

We restrict the electric transmission system's expansion to 20\% of its current capacity, acknowledging the challenges in inaugurating new transmission projects. The geographical spread of emissions from various industries is derived from~\cite{piamanzGeoreferencedIndustrialSites2018}, totaling 158~Mt \carbon{} annually.

@@

Addressing climate targets, we define three \carbon{} target scenarios:
\begin{itemize}
    \item[] Net-Zero: aligning with the EU's 2050 emission targets. Also denoted as NZ.
    \item[] Net-Negative~5\%: relative to 1990 emissions, equaling 230~Mt \carbon{}. Also denoted as NN~5\%.
    \item[] Net-Negative~10\%: relative to 1990 emissions, equaling 460~Mt \carbon. Also denoted as NN~10\%.
\end{itemize}
Unless otherwise mentioned, our reference is the Net-zero scenario. For 5\% Net-negative and 10\% Net-negative scenarios, the carbon sequestration potential is adjusted to 400~Mt/a and 600~Mt/a, respectively.

@@

\begin{figure*}[ht!]
    \centering
    \includegraphics*[width=\linewidth]{comparison/default/figures/90_nodes/cost_bar.png}
    \caption[short]{Total annual system cost for the European energy system for the different scenarios subdivided into groups of technologies. While the `Baseline' scenario has neither a \hydrogen{} or \carbon{} network, `Full' is allowed to expand both. "Gas Infrastructure" combines gas facilities for power and heat production, "H$_2$ Infrastructure" combines H$_2$ production, transport and re-electrification. The
    }
    \label{fig:cost_area}
\end{figure*}

@@

Figure~\ref{fig:operation_area_carbon_co2network} confirms our previous results and shows that FT synthesis production decreases with sequestration availability. At the same time, integrated carbon capture from Gas Combined Heat and Power (CHP) plants, Allam Cycle plants, Steam Methane Reforming (SMR) and DAC increases. Other technologies are constant across varying levels of sequestration due to different reasons: biomass is bound by its maximum available potential (as reported in~\cite{enspreso_database}); the industry processes with their associated emissions are set to fixed values; the methanol production is bound by a lower limit representing the demand from the shipping sector.
